---
title: "R_Kata_5"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(testthat)
require(MASS)
```
# 1. Some Egyptian fractions

Given a rational number n- n >= 0, with denominator strictly positive decompose 
this number as a sum of rationals with numerators equal to one and without 
repetitions (2/3 = 1/2 + 1/6 is correct but not 2/3 = 1/3 + 1/3, 1/3 is repeated).

The algorithm must be "greedy", so at each stage the new rational obtained in the 
decomposition must have a denominator as small as possible. In this manner the 
sum of a few fractions in the decomposition gives a rather good approximation of
the rational to decompose.

2/3 = 1/3 + 1/3 doesn't fit because of the repetition but also because the first 
1/3 has a denominator bigger than the one in 1/2 in the decomposition 2/3 = 1/2 + 1/6.

### Example

    decompose("21/23") --> "1/2,1/3,1/13,1/359,1/644046"
    
    
#### Note

1) The decomposition of 21/23 as

    21/23 = 1/2 + 1/3 + 1/13 + 1/598 + 1/897

is exact but don't fulfill our requirement because 598 is bigger than 359. Same for

    21/23 = 1/2 + 1/3 + 1/23 + 1/46 + 1/69 (23 is bigger than 13)
or 

    21/23 = 1/2 + 1/3 + 1/15 + 1/110 + 1/253 (15 is bigger than 13).

2) The rational given to decompose could be greater than one or equal to one, in
which case the first "fraction" will be an integer (with an implicit denominator of 1). 

```{r Write Function}
decompose <- function(n) {
  options(digits=22)
  
  # Return 'n' if it is a integer
  if (n %% 1 == 0 & n > 1) return(as.character(n))
  
  # Define vector to store results & set counter
  decomposition <- c(); return_str <- c(); i <- 2
  
  while(sum(decomposition) < n) {
    if ((n - (sum(decomposition) + 1/i)) >= 0) {
      decomposition <- c(decomposition, 1/i)
      return_str    <- c(return_str, paste0("1/", i))
    }
  i <- i + 1
  }
  return(paste(return_str, collapse = ","))
}
```

```{r Test it}
dotest <- function(n, expected) {
  actual <- decompose(n)
  expect_equal(actual, expected)
}

test_that("tests", {
  dotest(3/4, "1/2,1/4")
  dotest(12/4, "3")
})
```

# 2. Where my anagrams at?

What is an anagram? Well, two words are anagrams of each other if they both contain
the same letters.
For example:

    'abba' & 'baab' == true
    'abba' & 'baab' == true
    'abba' & 'abbba' == false
    'abba' & 'abca' == false
    
Write a function that will find all the anagrams of a word from a list. You will
be given two inputs a word and an array with words. You should return an array of
all the anagrams or an empty array if there are none. 
For example:

    anagrams('abba', ['aabb', 'abcd', 'bbaa', 'dada']) => ['aabb', 'bbaa']
    anagrams('racer', ['crazer', 'carer', 'racar', 'caers', 'racer']) => ['carer', 'racer']
    anagrams('laser', ['lazing', 'lazy',  'lacer']) => []
    
    
```{r Write the Function}
anagrams <- function(word, words) {
  
  # Get single letters & their freq of 'word' adn each element in 'words'
  word_letters <- table(strsplit(word, split = ""))
  words_letters <- lapply(words, function(x) table(strsplit(x, split = "")))
  
  # Compare letters & their freq of each element in 'words_letters' to 'word_letters'
  anagram_idx <- sapply(words_letters, function(x) isTRUE(all.equal(word_letters, x)))

  # Return elements of 'words' that are a anagram of 'word'
  words[anagram_idx]
}
```
```{r Test-it}
test_that("Sample Tests", {
  expect_equal(anagrams('abba', c('aabb', 'abcd', 'bbaa', 'dada')), c('aabb', 'bbaa'))
  expect_equal(anagrams('racer', c('crazer', 'carer', 'racar', 'caers', 'racer')), c('carer', 'racer'))
})
```
# 3. Primes in numbers

Given a positive number n > 1 find the prime factor decomposition of n. 
The result will be a string with the following form :
    
    "(p1**n1)(p2**n2)...(pk**nk)"
    
    where 'a ** b' means a to the power of b

with the p(i) in increasing order and n(i) empty if n(i) is 1.

Example: 
    
    n = 86240 should return "(2**5)(5)(7**2)(11)"
    
```{r Write the Function}
primeFactors <- function(n) {
  # Define index 'i' & vector 'res' to store the primes of the decomposition
  res <- c(); i <- 2
  
  # Do the factor decomposition for 'n'. Divide it by 'i' & if the result in a
  # round numeric, update n to n/i - repeat this producere until n < i
  while(n >= i) {
    if ((n / i) %% 1 == 0) {
      n = n / i
      res = c(res, i)
    } else {
      i = i + 1
    }
  }
  
  # If 'res' is null, 'n' is a prime -> no decomposition possible -> return 'n'
  # Else use 'res' to create the decomposition as a single string
  if (is.null(res)) {
    
    return(paste0('(', n, ')'))
  } else {
    
    tab_res <- table(res)
    
    ret_res <- paste(unlist(
      lapply(seq_along(tab_res), FUN = function(x) {
        paste0('(', names(tab_res[x]), "**" , tab_res[x], ')')
      }
      )), collapse = '')
    
    return(gsub('\\*\\*1)', ')',  ret_res))
  }
}
```

```{r Test-It}
testing <- function(n, expected) {
  actual <- primeFactors(n)
  expect_equal(actual, expected)
}

test_that("tests", {
  testing(7775460, "(2**2)(3**3)(5)(7)(11**2)(17)")
  testing(7919, "(7919)")
})
```
# 4. Last digit of a large number

Define a function that takes in two non-negative integers 'aaa' & 'bbb' and  
returns the last decimal digit of aba^bab.
Note that 'aaa' and 'bbb' may be very large!

### For example:
The last decimal digit of 9^7 is 0, as 9^7 = 4782969
The last decimal digit of (2^200)^(2^300), which has over 10^{92} decimal digits,
is 666.
Also, please take 0^0 to be 1.

You may assume that the input will always be valid.

### Examples:
    last_digit("4", "1")            # returns 4
    last_digit("4", "2")            # returns 6
    last_digit("9", "7")            # returns 9    
    last_digit("10","10000000000")  # returns 0
    
## Remark
Since R doesn't have native arbitrarily large integers, your arguments are going
to be strings representing non-negative integers instead.
    
```{r Write Function}
last_digit <- function(s1, s2) {
  if (s2 == 0) return(1)
  if (s1 == 0) return(0)

  s1 <- as.numeric(substr(s1, nchar(s1), nchar(s1)))
  s2 <- as.numeric(substr(s2, nchar(s2)-1, nchar(s2))) 
 
  if (s1 %in% c(0,1,5,6)) return(s1)
  if (s1 == 4) return(c(6,4)[s2 %% 2 +1])
  if (s1 == 9) return(c(1,9)[s2 %% 2 +1])

  if (s1 == 2) return(c(6,2,4,8)[s2 %% 4 +1])
  if (s1 == 3) return(c(1,3,9,7)[s2 %% 4 +1])
  if (s1 == 7) return(c(1,7,9,3)[s2 %% 4 +1])
  if (s1 == 8) return(c(6,8,4,2)[s2 %% 4 +1])
}
```


```{r Test-it}
expect_equal(last_digit("4", "1"), 4)
expect_equal(last_digit("4", "2"), 6)
expect_equal(last_digit("9", "7"), 9)
expect_equal(last_digit("10", "10000000000"), 0)
expect_equal(last_digit("1606938044258990275541962092341162602522202993782792835301376", "2037035976334486086268445688409378161051468393665936250636140449354381299763336706183397376"), 6)
expect_equal(last_digit("3715290469715693021198967285016729344580685479654510946723", "68819615221552997273737174557165657483427362207517952651"), 7)
```
  
  