---
title: "Exercises of difficulty 7 in R"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(testthat)
```

# 1. Even or Odd - Which is Greater?

Given a string of digits confirm whether the sum of all the individual even digits are greater than the sum of all the indiviudal odd digits. Always a string of numbers will be given.

    - If the sum of even numbers is greater than the odd numbers return: "Even is greater than Odd"- 
    - If the sum of odd numbers is greater than the sum of even numbers return: "Odd is greater than Even"
    - If the total of both even and odd numbers are identical return: "Even and Odd are the same"

```{r Write Function}
even_or_odd <- function(s){
    
    # Split 's' to its single numerics
    s_num <- as.numeric(strsplit(s, "")[[1]])
    
    # Get sums of even/ odd digits
    sum_even <- sum(s_num[s_num %% 2 == 0])
    sum_odd  <- sum(s_num[s_num %% 2 != 0])
    
    # Return Result of comparison between 'sum_even' & 'sum_odd'
    if (sum_even > sum_odd) return('Even is greater than Odd')
    if (sum_even < sum_odd) return('Odd is greater than Even')
    return('Even and Odd are the same')
}
```

```{r Test it}
test_that("Sample tests", {
  expect_equal(even_or_odd('12'), 'Even is greater than Odd')
  expect_equal(even_or_odd('123'), 'Odd is greater than Even')
  expect_equal(even_or_odd('112'), 'Even and Odd are the same')
})
```

# 2. Sum of Numbers

Given two integers a and b, which can be positive or negative, find the sum of all the integers between including them too and return it. If the two numbers are equal return a or b.

Note: a and b are not ordered!

#### Examples:

    get_sum(1, 0) == 1   # 1 + 0 = 1
    get_sum(1, 2) == 3   # 1 + 2 = 3
    get_sum(0, 1) == 1   # 0 + 1 = 1
    get_sum(1, 1) == 1   # 1 Since both are same
    get_sum(-1, 0) == -1 # -1 + 0 = -1
    get_sum(-1, 2) == 2  # -1 + 0 + 1 + 2 = 2
    
    
```{r Write Function}
get_sum <- function(a, b){
    if (a == b) {
        return(a)
    } else {
        return(sum(a:b))
    }
}
```
    
```{r Test it}
test_that("Example", {
  expect_equal(get_sum(0, 1), 1)
  expect_equal(get_sum(0, -1), -1)
})
```
    
    