---
title: "Exercises of difficulty 7 in R"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(testthat)
```

# 1. Even or Odd - Which is Greater?

Given a string of digits confirm whether the sum of all the individual even digits are greater than the sum of all the indiviudal odd digits. Always a string of numbers will be given.

    - If the sum of even numbers is greater than the odd numbers return: "Even is greater than Odd"- 
    - If the sum of odd numbers is greater than the sum of even numbers return: "Odd is greater than Even"
    - If the total of both even and odd numbers are identical return: "Even and Odd are the same"

```{r Write Function}
even_or_odd <- function(s){
    
    # Split 's' to its single numerics
    s_num <- as.numeric(strsplit(s, "")[[1]])
    
    # Get sums of even/ odd digits
    sum_even <- sum(s_num[s_num %% 2 == 0])
    sum_odd  <- sum(s_num[s_num %% 2 != 0])
    
    # Return Result of comparison between 'sum_even' & 'sum_odd'
    if (sum_even > sum_odd) return('Even is greater than Odd')
    if (sum_even < sum_odd) return('Odd is greater than Even')
    return('Even and Odd are the same')
}
```

```{r Test it}
test_that("Sample tests", {
  expect_equal(even_or_odd('12'), 'Even is greater than Odd')
  expect_equal(even_or_odd('123'), 'Odd is greater than Even')
  expect_equal(even_or_odd('112'), 'Even and Odd are the same')
})
```

# 2. Sum of Numbers

Given two integers a and b, which can be positive or negative, find the sum of all the integers between including them too and return it. If the two numbers are equal return a or b.

Note: a and b are not ordered!

#### Examples:

    get_sum(1, 0) == 1   # 1 + 0 = 1
    get_sum(1, 2) == 3   # 1 + 2 = 3
    get_sum(0, 1) == 1   # 0 + 1 = 1
    get_sum(1, 1) == 1   # 1 Since both are same
    get_sum(-1, 0) == -1 # -1 + 0 = -1
    get_sum(-1, 2) == 2  # -1 + 0 + 1 + 2 = 2
    
    
```{r Write Function}
get_sum <- function(a, b){
    if (a == b) {
        return(a)
    } else {
        return(sum(a:b))
    }
}
```
    
```{r Test it}
test_that("Example", {
  expect_equal(get_sum(0, 1), 1)
  expect_equal(get_sum(0, -1), -1)
})
```
  

# 2. A Rule of Divisibility by 7

A number m of the form 10x + y is divisible by 7 if and only if x − 2y is divisible by 7. In other words, subtract twice the last digit from the number formed by the remaining digits. Continue to do this until a number known to be divisible or not by 7 is obtained; you can stop when this number has at most 2 digits because you are supposed to know if a number of at most 2 digits is divisible by 7 or not.

The original number is divisible by 7 if and only if the last number obtained using this procedure is divisible by 7.

### Examples:

    1. m = 371 -> 37 − (2×1) -> 37 − 2 = 35
Thus, since 35 is divisible by 7, 371 is divisible by 7. The number of steps to get the result is 1.


    2. m = 1603 -> 160 - (2 x 3) -> 154 -> 15 - 8 = 7
Thus, since 33 is not divisible by 7, 372 is not divisible by 7. The number of steps to get the result is 1.

    3. m = 477557101 -> 47755708 -> 4775554 -> 477547 -> 47740 -> 4774 -> 469 -> 28
28 is divisible by 7, so is 477557101. The number of steps is 7.

### Task:

Your task is to return to the function seven(m) (m integer >= 0) an array (or a pair, depending on the language) of numbers, the first being the last number m with at most 2 digits obtained by your function (this last m will be divisible or not by 7), the second one being the number of steps to get the result.

### Examples:

    seven(371) should return [35, 1]
    seven(1603) should return [7, 2]
    seven(477557101) should return [28, 7]
    seven(109) should return [-8, 1]
    
    
```{r Write Function}
seven <- function(m) {
  # As long as m consists of more than two digits, remove the last digit and
  # substract it * 2 from the remaining numbe; define counter
  counter <- 0
  while (log10(abs(m)) >= 2) {
    
    # Split 'm' to its single digits
    m_str_split <- strsplit(as.character(m), split = "")[[1]]
    
    # Get the last digit of 'm' and the remaining number
    m_last_digit       <- as.numeric(m_str_split)[length(m_str_split)]
    m_remaining_digits <- as.numeric(paste(
      m_str_split[1:(length(m_str_split) - 1)], collapse = "")
      )
    
    # Update 'm'+ count 'counter' up
    m       <- m_remaining_digits - 2 * m_last_digit
    counter <- counter + 1
  }
  
  return(c(m, counter))
}
```

```{r TestIt}
testing <- function(m, expect) {
  s <- sprintf("%s", toString(m))
  cat(s, "\n")
  actual <- seven(m)
  cat("actual:\n ", actual, "\n")
  cat("expect:\n ", expect, "\n")
  expect_equal(actual, expect)
}

test_that("fixed tests", {
  testing(1021, c(10, 2))
  testing(477557101, c(28, 7))
  testing(477557102, c(47, 7))
  
})

```
