---
title: "Exercises of difficulty 8 in R"
output: html_document
---

## Load needed Packages and set the 'Rmd' file up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(testthat)
```

# 1. Reversed Strings
Complete the solution so that it reverses the string passed into it.  
Example:

    'world'  =>  'dlrow'

```{r Write the Function}
solution <- function(s) {
    s_split         <- strsplit(s, split = "")[[1]]
    s_split_reverse <- rev(s_split)
    return(paste(s_split_reverse, collapse = ""))
}
```

```{r Test it}
test_that("example", {
  expect_equal(solution('world'), 'dlrow')
  expect_equal(solution('hello'), 'olleh')
  expect_equal(solution(''), '')
  expect_equal(solution('h'), 'h')
})
```

# 2. Beginner Series - Clock
Clock shows 'h' hours, 'm' minutes and 's' seconds after midnight.  
Your task is to make 'Past' function which returns time converted to milliseconds.  

Example:

    past(0, 1, 1) == 61000
    
Input constraints:

    0 <= h <= 23, 0 <= m <= 59, 0 <= s <= 
    
    
```{r Write Function}
past <- function(h, m, s) {
    s_total <- s + 60 * m + 3600 * h # Convert time to seconds
    return(s_total * 1000)           # Convert seconds to milliseconds
}
```

```{r Test it}
test_that("basic tests", {
  expect_equal(past(0, 1, 1), 61000)
  expect_equal(past(1, 1, 1), 3661000)
  expect_equal(past(0, 0, 0), 0)
  expect_equal(past(1, 0, 1), 3601000)
  expect_equal(past(1, 0, 0), 3600000)
})
```

# 3. Square(n) Sum
Complete the square sum function so that it squares each number passed into it 
and then sums the results together.  

For example:
    
    [1, 2, 2] should return 9 because 1^2 + 2^2 + 2^2 = 9.
```{r Write Function}
square_sum <- function(nums) {
    return(sum(nums^2))
}
```
```{r Test it}
test_that("basic tests", {
  expect_equal(square_sum(c(1, 2)), 5)
  expect_equal(square_sum(c(0, 3, 4, 5)), 50)
  expect_equal(square_sum(c()), 0)
  expect_equal(square_sum(c(-1, -2)), 5)
  expect_equal(square_sum(c(-1, 0, 1)), 2)
})
```