---
title: "Exercises of difficulty 6 in R"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(testthat)
```

# 1. PI approximation

The aim of the kata is to try to show how difficult it can be to calculate decimals of an irrational number with a certain precision. We have chosen to get a few decimals of the number "pi" using the following infinite series (Leibniz 1646–1716):

     PI / 4 = 1 - 1/3 + 1/5 - 1/7 + ... which gives an approximation of PI / 4.
     --> see: http://en.wikipedia.org/wiki/Leibniz_formula_for_%CF%80
     

To have a measure of the difficulty we will count how many iterations are needed to calculate PI with a given precision.

There are several ways to determine the precision of the calculus but to keep things easy we will calculate to within epsilon of your language Math::PI constant. In other words we will stop the iterative process when the absolute value of the difference between our calculation and the Math::PI constant of the given language is less than epsilon.

Your function returns an array or an arrayList or a string or a tuple depending on the language (See sample tests) where your approximation of PI has 10 decimals

Example :

    your function calculates 1000 iterations and 3.140592653839794 but returns:
    iter_pi(0.001) --> [1000, 3.1405926538]

Unfortunately, this series converges too slowly to be useful, as it takes over 300 terms to obtain a 2 decimal place precision. To obtain 100 decimal places of PI, it was calculated that one would need to use at least 10^50 terms of this expansion!
```{r Write Function}
iterPi <- function(epsilon) {
    pi_current = 4
    if (abs(pi_current - pi) <= epsilon) return(c(0, round(pi_current, 10)))
    for (i in 2:1e+6) {
        if (i %% 2 != 0) {
            pi_current <- pi_current + 4/(2 * i - 1)
        } else {
            pi_current <- pi_current - 4/(2 * i - 1)
        }
        if (abs(pi_current - pi) <= epsilon) return(c(i, round(pi_current, 10)))
    }
}
```

```{r Test It}
testing <- function(eps, expected) {
  actual <- iterPi(eps)
  # there is a tolerance
  expect_equal(actual, expected, tol = 1e-10, scale =  1, info = )
}

test_that("test iterPi", {
  testing(0.1, c(10, 3.0418396189))
  testing(0.01, c(100, 3.1315929036))
  testing(0.001, c(1000, 3.1405926538))
})
```
# 2. Find the missing term in an Arithmetic Progression

An Arithmetic Progression is defined as one in which there is a constant difference between the consecutive terms of a given series of numbers. You are provided with consecutive elements of an Arithmetic Progression. There is however one hitch: exactly one term from the original series is missing from the set of numbers which have been given to you. The rest of the given series is the same as the original AP. Find the missing term.

You have to write a function that receives a list, list size will always be at least 3 numbers. The missing term will never be the first or last one.

#### Example

    findMissing([1, 3, 5, 9, 11]) == 7

PS: This is a sample question of the facebook engineer challenge on interviewstreet. I found it quite fun to solve on paper using math, derive the algo that way. Have fun!
```{r Write Function}
find_missing <- function(sequence){
    
    # Get the differences between all following values in sequence
    differences <- sapply(2:length(sequence), function(x) sequence[x] - sequence[x -1])
    
    # Create Table of differences
    diff_table <- table(differences)

    # Get the difference between following values in sequence that is not matching
    # (appears only once) & the matching difference between following values in sequence 
    # (appears at least twiche)
    no_match_diff <- as.numeric(names(diff_table)[diff_table == 1])
    match_diff    <- as.numeric(names(diff_table)[diff_table > 1])
    
    # Get the missing value, by going to the entry that has an unmachting difference
    return(sequence[differences == no_match_diff][1] + match_diff)
}
```
```{r Test it}
test_that("Example Test", {
  expect_equal(find_missing(c(1, 2, 3, 4, 6, 7, 8, 9)), 5)
})
```

# 3. Sum of many ints

Write this function: 
    
    f(n, m) = Sum from i = 1, to n: i %% m
    
for i from 1 to n, do i % m and return the sum

### Example

    f(n=10, m=5)
    --> returns 20 (1+2+3+4+0 + 1+2+3+4+0)
    
Note: You'll need to get a little clever with performance, since n can be a very large number
    
```{r Write Function}
f <- function(n, m){
  # Create sequence from 1:n and do modulo operation on each element,
  # then sum up all these elements
  sum(sapply(1:n, FUN = function(x) x %% m))
}
```

```{r Test it}
test_that("Example Tests", {
  expect_equal(f(10, 5), 20)
  expect_equal(f(20, 20), 190)
  expect_equal(f(15, 10), 60)
})
```

